---
title: "Sandbox: Use LDSC to assess factorization"
output: html_notebook
---
```{r setup, echo  = FALSE}
pacman::p_load(data.table, tidyr, dplyr, readr, ggplot2, stringr)
source("./assessment_functions.R")
  T="/work-zfs/abattle4/ashton/snp_networks/custom_l1_factorization/"
  args <- list()
  args$factors <- paste0("/work-zfs/abattle4/ashton/snp_networks/custom_l1_factorization/factorization_data/beta_se_fixed_first900_900.factors.txt")
  args$factors <- paste0("/work-zfs/abattle4/ashton/snp_networks/custom_l1_factorization/factorization_data/aug_28.ssvd.factors.txt")
  args$ldsc_reference <-"/work-zfs/abattle4/ashton/snp_networks/scratch/ldsc_all_traits/ldsc_results/seed2_thres0.9_h2-0.1/"
  args$ldsc_dir <-paste0(T,"/results/beta_se_fixed_first900_900/ldsc_enrichment_Multi_tissue_chromatin/" ) 
  args$trait.ids <- "/work-zfs/abattle4/ashton/snp_networks/gwas_decomp_ldsc/trait_selections/seed2_thresh0.9_h2-0.1.studies.tsv"
  args$trait.names <- "/work-zfs/abattle4/ashton/snp_networks/gwas_decomp_ldsc/trait_selections/seed2_thresh0.9_h2-0.1.names.tsv"
  args$n_overlap <- 2
```


### And putting it all together
```{r}
#Read in#Read in
ldsc.reference <- readInLDSC(args$ldsc_reference)

factorization.enrichment <- readInLDSC(args$ldsc_dir, type = "factorization enrichment")
tissue.labels <- fread("/work-zfs/abattle4/ashton/snp_networks/custom_l1_factorization/ldsc_reference/finucane_2018_supp_table7.ashton.csv")

factorization <- fread("/work-zfs/abattle4/ashton/snp_networks/custom_l1_factorization/factorization_data/PMA_91_2.3_8-11.factors.txt")

trait.names <- scan("/work-zfs/abattle4/ashton/snp_networks/gwas_decomp_ldsc/trait_selections/seed2_thresh0.9_h2-0.1.names.tsv", what = character())
trait.studies <- scan("/work-zfs/abattle4/ashton/snp_networks/gwas_decomp_ldsc/trait_selections/seed2_thresh0.9_h2-0.1.studies.tsv", what = character())
```
AFter today's meeting with Alexis, trying a new, simpler metric
Just keep track of all the pairwise relationships between traits- if they share and if they don't. Track this

```{r}
fdr.thresh <- 0.05
sharing <- matrix(0, length(trait.names), length(trait.names))
for(t in trait.studies)
{
  curr.t <- unique((ldsc.reference %>% filter(Source == t, within_trait_FDR < fdr.thresh))$tissue)
  if(length(curr.t) == 0) #no matches can occur
  {
    next
  }
  matches <-ldsc.reference %>% filter(within_trait_FDR < fdr.thresh, tissue %in% curr.t) %>% group_by(Source) %>% 
    slice(which.min(within_trait_FDR)) %>% ungroup()
  #^ we allow for matchin with onese self, makes downstream easier. Just omit it.
  curr.i <- which(t == trait.studies)
  match.i <- sapply(matches$Source, function(j) which(j == trait.studies))
  sharing[curr.i, match.i] <- 1
}
print(sharing)
```
Look at the natural clustering of this....
```{r}
pca <- prcomp(x = t(sharing[-c(36,41,54),]), center = TRUE, scale. = TRUE)
plot(pca)
which(colSums(sharing) == 0)
names(pca)
plot(pca$x[,1], pca$x[,2])
```
Hierarchical clustering...
```{r, fig.width=15}
library(dendextend)
rownames(sharing) <- trait.names
h <- hclust(dist(sharing))
dend <- as.dendrogram(h)
labels_colors(dend) <- NULL
dend2 <- color_labels(dend, k = 15)
dend2 <- set(dend2, "labels_cex", 1)
par(mar = c(1,1,1,13))
plot(dend2, horiz = TRUE)
```

Interesting. Some of these groupings make sense, some do not.
This may not be the most meaningful way to detect trait similarity, but can help us.
Question- which traits have the least overlap? which have the most?
```{r}
#smallest matching guy?
trait.names[rowSums(sharing)==0]
trait.names[which.max(rowSums(sharing))]

```

Now, calculate a score and a confusion matrix for each factor:
```{r}
check.list <- apply(factorization, 2, function(x) which(x != 0))
#These all go together: this assumes (j-1)*j/2 total associations
#True number would by sum of matrix - j/2
true <- sharing[check.list[[1]], check.list[[1]]] #what the actual relationship between these tissues is
true[lower.tri(pred, diag = TRUE)] <- NA #only want the upper triangle
score <- sum(true == 1,na.rm = TRUE) - sum(true == 0, na.rm = TRUE)
simpleScore <- function(vect, m)
{
  true <- m[vect,vect] #what the actual relationship between these tissues is
  true[lower.tri(true, diag = TRUE)] <- NA #only want the upper triangle
  #assume our guess is all in here should be one
  sum(true == 1,na.rm = TRUE) - sum(true == 0, na.rm = TRUE)
  #The ones we guessed right in the group - the ones we didn't
}
#I think maybe this is the way to go?
simpleNorm <- function(vect, m)
{
  true <- m[vect,vect] #what the actual relationship between these tissues is
  t <- true[lower.tri(true, diag = FALSE)] #only want the upper triangle
  all.ones <- matrix(1, length(vect), length(vect))
  p <- all.ones[lower.tri(all.ones, diag = FALSE)]
  sqrt(sum((t-p)^2))
  #The ones we guessed right in the group vs the ones we didn't
}

```
Putting it all together
```{r}
fact.scores <- sapply(check.list, function(v) simpleScore(v, sharing))
fact.dist <- sapply(check.list, function(v) simpleNorm(v, sharing))
plotFactors(factorization, trait.names, title = "refresh",cluster = TRUE)
plot(fact.scores)
plot(fact.dist)

```

Confusion matrix?
This is a bit harder...

